% !TEX root = MAIN.tex

\chapter{Executive Summary}

This document is a report on the assessment of the ASN.1 test suite quality based on code-driven mutation testing via MASS and SEMuS. The source code that we analyzed was the auto-generated source code by the ASN.1 compiler, rather than in ASN1SCC software itself. On this analysis, we used ASN1SCC commit \texttt{b971b12ecbe4d07e9c86e8b330bb34f8d6d203fc}. For the given grammar, the size of the auto-generated source code is 4\,338 LOC. While the unit test suite consists of 107 auto-generated test cases.

We performed the analyses with MASS and SEMuS; MASS is a mutation analysis tool for space software, while SEMuS is a test suite augmentation tool based on mutation testing. Both tools has been developed within the context of the FAQAS project.

We provide in this report (1) the configuration we used to setup our toolset with ASN.1 (2) the results of the code-driven mutation analysis process, (3) information about the test cases generated based on mutation testing, and the (4) set of mutants not killed by the approach.


% \section{Applicable and reference documents}

% \begin{itemize}
% \end{itemize}

\chapter{Terms, definitions and abbreviated terms}

\begin{itemize}
\item{FAQAS}: activity ITT-1-9873-ESA.
\item{FAQAS-framework}: software system to be released at the end of WP4 of FAQAS.
\item{MASS}: Toolset for Mutation Analysis for Space Software.
\item{SEMuS}: Toolset for Mutation Testing for Space Software.
\item{SUT}: Software under test, i.e, the software that should be mutated by means of mutation testing.

\end{itemize}

\clearpage
