% !TEX root = MAIN.tex

\chapter{Software Overview}
\label{chapter:overview}

\section{Function and Purpose}

The FAQAS activity concerns the investigation of mutation testing as a method to evaluate the quality of software test suites and mutation testing as a method to derive new software test cases. 

The \FAQAS implements a toolset supporting code-driven and data-driven mutation testing that integrates and extends state-of-art solutions. The proposed methodology enables a scalable and accurate mutation testing process even when the software under test is large and characterized by test suites requiring long execution time.

Since \FAQAS implements two distinct features, code-driven mutation testing and data-driven mutation testing, the functional requirements contains two separate sections, each one concerning one of the two features: Section~\ref{sec:codeDriven} concerns code-driven mutation testing, Section~\ref{sec:dataDriven} concerns data-driven mutation testing.

The requirements defined in this chapter are univocally identified by the paragraph id appearing on the left.

\section{General Capabilities}

\RQ{} \FAQAS shall support test suite evaluation based on code mutation.

\RQ{} \FAQAS shall support test suite augmentation based on code mutation.

\RQ{} \FAQAS shall support test suite evaluation based on data mutation.

\RQ{} \FAQAS shall support test suite augmentation based on data mutation.


\section{General Constraints}

\RQ{} The automated generation of test cases (i.e., the objective of test suite augmentation) shall rely on existing tools because the automated generation of test cases is an open, complex, research problem.  

\RQ{} The automated generation of test cases for code-mutation shall rely on KLEE, which is the most stable test case generation tool, based on WP2 evaluation.

\RQ{} \FAQAS shall partially support test generation for system-level test cases for the data-driven mutation testing.


\section{Software Architecture}

\RQ{} \FAQAS shall follow a modular architecture.

\section{Operational Environment}

\RQ{} The \FAQAS shall run on x86-64 processor architectures and HPC infrastructures.

\RQ{} The \FAQAS shall be executed on the following minimum hardware specifications: 4 GB RAM and 10 GB of free disk space.

\RQ{} The \FAQAS shall be executed on a Linux operating system with a Bash shell.

\RQ{} The \FAQAS shall support the following Linux distributions: (i) Debian 9, (ii) Ubuntu 16, and (iii) CentOS 7.

\section{Assumptions and dependencies}

\RQ{} The \FAQAS shall support SUT built using either GCC Make~\footnote{https://gcc.gnu.org/onlinedocs/gccint/Makefile.html} or WAF\footnote{https://waf.io/}.

\RQ{} The \FAQAS shall support SUT compiled with GCC~\footnote{https://gcc.gnu.org}.

\RQ{} The \FAQAS shall support SUT test suites implemented as scripts (hereafter, \emph{test suite script}) that trigger the execution of test cases (each test case is executed in a separate process). Test suite scripts could be implemented either as Makefiles or a Bash scripts. Each test case is executed through the invocation of a command in the script.



\chapter{Requirements}

\section{Functional requirements}
\label{sec:requirements}

\input{codeDriven}
\input{dataDriven}



\section{System interface requirements}

\RQ{} The \FAQAS shall use the command line as main user interface.

\RQ{} \FAQAS shall support SUT test harness Google Test\footnote{https://github.com/google/googletest} and the Basic mathematical Library Test Suite (BLTS)\footnote{https://essr.esa.int/project/mlfs-mathematical-library-for-flight-software}.

\RQ{} The engineer shall configure the \FAQAS by editing a file to set multiple environment variables that shall enable the mutation testing process.



\section{Adaptation and missionization requirements}

\RQ{} \FAQAS shall not be used in mission.

\RQ{} \FAQAS shall be used only to support development, validation, and verification activities in the development environment. 




\section{Computer resource requirements}


\RQ{} The \FAQAS shall support Linux operating systems.



\section{Security requirements }

\RQ{} \FAQAS shall no use network connections.

\section{Safety requirements}

\RQ{} \FAQAS shall not be used to assess test cases that are executed with target hardware in the loop, to avoid safety hazards.

\section{Reliability and availability requirements}

\RQ{} \FAQAS shall work according to is functional specifications every time it is invoked.

% \RQ{} The system is expected to work according to is functional specifications every time it is invoked.

\RQ{} \FAQAS shall not provide an upper bound for mutation testing execution time.

\remark Mutation testing execution time depends on both the number of mutants to be executed and the duration of the test suite execution, information that cannot be foreseen before execution.

\section{Quality requirements}

\RQ{} Usability. Software engineers (i.e., professionals with a master degree in informatics or related fields) shall be able to successfully use the software after reading its documentation.

\RQ{} \FAQAS shall be used in any environment matching the characteristics indicated in this document.

\RQ{} \FAQAS shall comply with software development standards. The software development process shall follow ECSS guidelines as per SoW.


\section{Design requirements and constraints}

\RQ{} \FAQAS shall be released with ESA Software Community Licence Permissive – v2.3, as defined at https://essr.esa.int/. Any reused component should be compatible with the abovementioned licence.

\RQ{} \FAQAS shall be implemented using the bash shell script language, the Python programming language, and the C/C++ programming language.

\RQ{} \FAQAS shall mutate the source code of the SUT not the intermediate representation.


\section{Adaptation and installation requirements}

% - Deployment methods (it is maybe a bit early, but we have to think on the methodology to deploy the tool e.g. compile it, have it delivered with an installer, on a container, etc)

% 
\RQ{} \FAQAS can be installed using an installer that shall be provided by the SnT.


\section{Software operations requirements}

\RQ{} \FAQAS shall be executed at anytime, 
%It should be possible to execute the system anytime, 
in an environment matching the characteristics indicated in this document.

\section{Software maintenance requirements}

\RQ{} One year maintenance support shall be provided as per SoW.

\section{System and software observability requirements}

\RQ{} The debugging of the \FAQAS shall be possible, if and only if 
%To enable post-mortem debugging, 
all the temporary files generated by the system are kept.

\chapter{Verification, validation and system integration}
 \section{Verification and validation process requirements}
 
\RQ{} Every mutation operator shall be tested by a dedicated unit test case.
 
 \RQ{} A system test suite for the Code-Driven Mutation Testing component shall be provided. The test suite shall be based on the MLFS case study (see D2).
 
 \RQ{} \FAQAS shall enable the correct computation of the mutation score for the FAQAS case study systems indicated in deliverable D2.
 
 \subsection{Validation approach}

\RQ{} SnT shall perform a preliminary validation of the delivered framework.

\RQ{} FAQAS industry partners shall use the system at their premises to validate it.
