% !TEX root = MAIN.tex

\chapter{ECSS Tailoring}

\REVTOOL{P-06}{From the Negotiation Meeting (MoM Signed)  ITT-1-9873-ESA-Negotiation.Minutes, ESA and SnT agreed that the general approach for developing the FAQAS framework is specified in the following. }

\begin{itemize}
\item To specify the product, there is only need for one level of specifications, for this reason RB with a proper level of detailed will be provided.
The specification documents to be delivered in this regard are SSS and IRD.

\item SnT will develop unit tests for the code developed by SnT.
The specification documents to be delivered in this regard are Unit/Integration Test Plan and Test Reports

\item SnT will develop system tests based on the RB; more precisely, the system tests will consist of the execution of the framework against the case study systems selected for the project.
The specification documents to be delivered in this regard are \emph{SW Validation Specification} and \emph{SW Validation reports}.

\item Since the project will make use of existing software components the ECSS requirements related to software reuse apply.
The specification documents to be delivered in this regard is the \emph{SW Reuse File}.

\item Specification and validation documentation are required. Specifications of \emph{development plan}, \emph{validation plan}, \emph{verification plan}, \emph{maintenance plan}, \emph{product assurance plan} will be combined in a single document.

\item For ECSS software reviews the project will follow the activity review plan; the reviews will be performed according to ECSS practices.

\item Concerning ECSS-Q-ST-80C the project will adhere to requirements on \emph{configuration management}, \emph{bug tracking}, \emph{product metrics}.

\item Other specification documents to be produced are \emph{SDD}, \emph{SCF}, \emph{SRelD}, and \emph{SUM}.
\end{itemize}

\REVFINAL{A12}{Detailed tailoring information is provided in Appendix~\ref{appendix:tailoring}.}

% The document is missing: 
% SW verification plan, development plan, maintenance plan, product assurance plan
