\chapter{Software validation testing specification design}

\section{General}

In the following the specification testing for every requirement will be detailed, following the structure underlined by the chapters of the SSS.
Every requirement is univocally identified.

\section{Software Overview}
The requirement in this section describes the general capabilities of the software, the general constraints, and the software architecture.
They are available in the SSS (Chapter 3).
The testing procedures are detailed in Table~\ref{tables:overview}.

\input{tables/sw_overview}

\section{Requirements}

The requirements in this section comprise the following categories, one for every section of chapter 4 of the SSS.

\begin{itemize}
  \item Functional requirements
  \item System interface requirements
  \item Adaptation and missionization requirements
  \item Computer resource requirements
  \item Security requirements
  \item Safety requirements
  \item Reliability and availability requirements
  \item Quality requirements
  \item Design requirements and constraints
  \item Adaptation and installation requirements
  \item Software operations requirements
  \item Software maintenance requirements
  \item System and software observability requirements
\end{itemize}

 Every category will be detailed in the following tabulars.

\subsection{Functional Requirements}

The functional requirements are relative to four procedures belonging to the FAQAS framework:
\begin{itemize}
  \item \emph{Test Suite Evaluation Based on Code-driven Mutation} here reported for readablity as \emph{Code-driven Evaluation}
  \item \emph{Test Suite Augmentation Based on Code-driven Mutation} here reported for readablity as \emph{Code-driven Augmentation}
  \item \emph{Test Suite Evaluation Based on Data-driven Mutation} here reported for readablity as \emph{Data-driven Evaluation}
  \item \emph{Test Suite Augmentation Based on Code-driven Mutation} here reported for readablity as \emph{Data-driven Augmentation}
\end{itemize}

The test for \emph{Code-driven Evaluation} and \emph{Code-driven Augmentation} are detailed in Table~\ref{tables:code}.

\input{tables/requirements_code}

The test for \emph{Data-driven Evaluation} and \emph{Data-driven Augmentation} are detailed in Table~\ref{tables:data}.

\input{tables/requirements_data}

\subsection{System Interface requirements}

Table~\ref{tables:interface} details the validation testing procedures for System interface requirements.

\input{tables/requirements_interface}

\subsection{Others}

Table~\ref{tables:others} details the validation testing procedures for all the other categories of this section of requirements.

\input{tables/requirements_other}

\section{Verification, validation and system integration}

This section covers the validation testing procedures for the requirement contained in Chapter 5 of the SSS.

They are reported in Table~\ref{tables:verification}.

\input{tables/verification_validation}
