% !TEX root = MAIN.tex

\chapter{DAMAt - Software Unit Testing Approach}
\label{chap:approach_DAMAt}


\section{Unit Testing Strategy}

% Unit testing aims to verify that the functional requirements of DAMAt units are correctly implemented; test inputs are identified through the category-partition method.
Unit testing aims to verify that the functional requirements of DAMAt units are correctly implemented; test inputs are identified through the category partition method.


\section{Tasks and Items under Test}

Testing concerns the data-driven mutation API of DAMAt, from now on defined as \emph{DDMutation}, which handles the \emph{Mutate Data} activity.
The API can be divided into two separate units: \emph{DDMutationData} which reads the target data from the buffer and write it back in once is mutated, and \emph{DDMutationFault} which applies the selected mutation operator to the data.

\section{Feature to be tested}

Testing concerns verifying the correct behavior of the \emph{DDMutationData} and \emph{DDMutationFault} units implemented in \emph{DDMutation}, with regards to the instructions contained in the fault model and data model provided by the user, and to the C data type of the buffer targeted by the mutation.

\section{Feature not to be tested}

\DONE{I modified it; it seemed we did not test something important}
%Testing does not concern the verification of the capability of \emph{DDMutation} to handle every possible numeric parameter that could be specified by the user in the fault model and data model, since the number of possible combinations would render such a pursuit highly impractical if not impossible.
%It is instead based on realistic use cases and inputs.
%In the same way, testing do not cover every possible value that the buffer data that could be targeted by a mutation operator could assume.
Testing does not concern the verification of the capability of \emph{DDMutation} to handle every possible value stored in the data buffer. It is instead based on realistic use cases and inputs.

\section{Test Pass - Fail Criteria}

\emph{DDMutation} passes its tests if all the following are true:
\begin{itemize}
	\item Every test case is executed
	\item All test cases pass
	\item Exceptions and unexpected messages do not appear on screen and logs.
\end{itemize}

\section{Manually and Automatically Generated Code}

Part of the \emph{DDMutation} code is automatically generated for every specific \emph{FAQAS fault model} (see D2). This code and the relative generation process are tested organically with the rest of the API.
