% !TEX root = MAIN.tex

\chapter{Introduction}

This document is the Software Unit Test Plan of the software delivered by the ESA activity ITT-1-9873-ESA (i.e., the \emph{FAQAS framework}). Its purpose is to describe the unit testing activities to be done for the \FAQAS.
The FAQAS framework consists of the following software: a toolset  implementing code-driven mutation analysis (MASS), a toolset implementing code-driven test generation, a toolset implementing data-driven mutation analysis, a toolset implementing data-driven test generation.

This document follows a structure derived from tailoring of the structure proposed in ECSS-E-ST-40C Annex K. Tailoring has been adopted to clearly describe differences in the procedures adopted for the different components of the \FAQAS. More precisely, our tailoring adheres to the following directives:

\begin{itemize}
\item Sections 
\emph{K.1 - Introduction}, 
\emph{K.2 - Applicable and reference documents}, 
\emph{K.3 - Terms, definitions and abbreviated terms}, which are generic, are reported following the structure suggested in ECSS-E-ST-40C. 

\item Sections \emph{K.4 - Software overview}, \emph{K.5 - Software unit testing}, 
 and \emph{K.6 - Control procedures for software unit testing} are reported following the structure suggested in ECSS-E-ST-40C. They describe the procedures followed concern all the components of the \FAQAS.
 
\item Sections \emph{K.7 - Software unit testing approach}, 
\emph{K.8 - Software unit test test design},
 \emph{K.9 - Software unit test case specification},
 and \emph{K.10 - Software unit test procedures} are repeated multiple times, once for each tested component of the \FAQAS\footnote{Issue 1 contains only MASS}. 
 
\item Section \emph{K.11 - Software test plan additional information} appears once and covers al the components of the \FAQAS.
\end{itemize}
 
\chapter{Applicable and reference documents}

\begin{itemize}
\item{D1 - Mutation testing survey}
\item{D2 - Study of mutation testing applicability to space software}
\item{SSS - Software Systems Specifications}
\item{SUM - Software User Manual}
\item{SVS - Software Validation Specifications}
\item{For reference and terminology on category-partition method. Young, M., Pezze, M. (2005). Software Testing and Analysis: Process, Principles and Techniques. John Wiley and Sons, Inc.}
\end{itemize}

\chapter{Terms, definitions and abbreviated terms}

\begin{itemize}
\item{FAQAS}: activity ITT-1-9873-ESA
\item{FAQAS-framework}: software system to be released at the end of WP4 of FAQAS
\item{D2}: Deliverable D2 of FAQAS, \emph{Study of mutation testing applicability to space software}
\item{KLEE}: Third party test generation tool, details are provided in D2.
\item{SUT}: Software under test, i.e, the software that should be mutated by means of mutation testing.
\item{WP}: Work package
\end{itemize}

\clearpage
 

