% !TEX root = MutationTestingSurvey.tex

\section*{Revisions}
\label{sec:revisions}


\setlength\LTleft{0pt}
\setlength\LTright{0pt}
\tiny 
%@{\extracolsep{\fill}}
\begin{longtable}{|p{2cm}|p{1cm}|p{1.5cm}|p{9cm}|@{}}
\label{table:codeoperators} \\
\hline
\textbf{Issue Number}&\textbf{Date}&\textbf{Authors}&\textbf{List of changes}\\
\hline
ITT-1-9873-ESA-FAQAS-D1
Issue 3&
March 13th, 2020&
Fabrizio Pastore, Oscar Cornejo&
\begin{minipage}{8cm}
The following sections had been added:
\begin{itemize}
\item \ref{sec:testGeneration} Building Blocks of the Code-driven Automated Test Suites Augmentation Process.
\item \ref{sub:mutationscore} Analysis of Mutation Testing Results and Mutation Score Calculation.
\item \ref{sec:testGenerationData} Building Blocks of the Data-driven Automated Test Suites Augmentation Process.
\end{itemize}

The structure of the deliverable (i.e., order of sections) has been updated to simplify the reading (i.e., Sections 1.2 and 2.2 had been renamed an restructured).
\end{minipage}
\\
\hline
ITT-1-9873-ESA-FAQAS-D1
Issue 4
&March 30th, 2020
&Fabrizio Pastore, Oscar Cornejo
&
\begin{minipage}{8cm}
The following sections had been added:

\begin{itemize}
	\item~\ref{chapter:industry} Mutation Testing Benchmarks
	\item~\ref{chapter:trends} Mutation Testing Trends
\end{itemize}



In addition, we have addressed ESA comments provided on date March 3rd, 2020. Modified text appears in blue with annotations containing a reference to the comment. The list of comments with a discussion of the changes made is provided in Section~\ref{sec:ESA:comments:1}. Our changes include the addition of a set of mutation testing examples:
\begin{itemize}
	\item Listings~\ref{isPalindrome} to \ref{isPalindrome_TS_improved}
	\item Listings~\ref{equivalentexample} and \ref{equivalentmutantexample}
	\item Listings~\ref{redudantexample1} and \ref{redudantexample2}	
	\item Listings~\ref{midval} to \ref{example}
	\item Figure~\ref{fig:DataDrivenSimpleExample}
	\item Listings~\ref{JSONgrammar} to \ref{JSONfile}
	\item Listing~\ref{mutatedJSONfile}
	\item Listing~\ref{TestJSON}
\end{itemize}

\end{minipage}

\\
\hline
ITT-1-9873-ESA-FAQAS-D1
Issue 5
&April 16th, 2020
&Fabrizio Pastore, Oscar Cornejo
&
\begin{minipage}{8cm}

The following changes had been made (tracked in red):
\begin{itemize}
	\item Extracted Tables~\ref{table:operators:blindTransmissions} and \ref{table:operators:blindMemory} from Table \ref{table:dataOperators} to simplify the reading.
	\item Reorganized (new subsections) Section~\ref{sec:data_operators} to better follow the content of Table \ref{table:dataOperators}.
	\item Added Table~\ref{equivalentexample} to provide additional information about Peach.
	\item Addressed comments provided on 03.04.2020 by ESA (necessary to pass state-of-the-art review).
\end{itemize}

\end{minipage}

\\
\hline
ITT-1-9873-ESA-FAQAS-D1
Issue 6
&April 23rd, 2020
&Fabrizio Pastore, Oscar Cornejo
&
After agreement with ESA, we cleaned up the document by removing inline comments put to track responses to reviews.

\\

%Comment #2:
%When generating the pdf file, make sure to have the index of the document on the left, so that the document is easier to navigate.
%Author: Pedro Barrios Subject: Sticky Note Date: 28/02/2020, 09:18:06
%Comment #3:
%Try to make the document a bit more friendly to read (e.g. by adding some sentences in bold (see the highlighted ones for this paragraph), making bigger
%separation between paragraphs, ...)
%Author: Pedro Barrios Subject: Sticky Note Date: 28/02/2020, 09:18:11
%Comment #4:
%It is perhaps interesting to add a chapter with some basic definitions?
%e.g. equivalent mutant, redundant mutant, mutation score, killed mutant, live mutant, weak mutation, ...
%Author: Pedro Barrios Subject: Sticky Note Date: 28/02/2020, 09:18:18
%Comment #5:
%Please, consider to add more examples.

\hline                                                           
\end{longtable}
\normalsize

\clearpage