% !TEX root = MAIN.tex

\chapter{Executive Summary}

This document is a report on the issues identified by applying Data-driven Mutation Analysis on the \case using the \DAMA tool, which has been developed in the context of the \FAQAS.

\DAMA is a data-driven mutation analysis tool. It generates mutants by modifying the data contained in the SUT buffers through the insertion in the source code of Mutation Probes. The mutation probes generate mutants following mutation operators defined in a Fault Model.

The code we analyzed was the ESAIL SVF test suite, which evaluates the ESAIL OBSW and in particular the test cases regarding the interaction between the PDHU (Payload Data Handling Unit) component and the OBSW (On-Board Software).


\section{Terms, definitions, and abbreviated terms}

\begin{itemize}
\item{FAQAS}: activity ITT-1-9873-ESA
\item{FAQAS-framework}: software system to be released at the end of WP4 of FAQAS.
\item{SUT}: Software under test, i.e, the software that should be mutated using mutation testing.
\item{FMC}: Fault model coverage, the percentage of fault models covered by the test suite.
\item{MOC}: Mutation operation coverage, the percentage of data items that have been mutated at least once, considering only those that belong to the data buffers covered by the test suite.
\item{MS}: Mutation Score, the percentage of mutants killed by the test suite (i.e., leading to at least one test case failure) among the mutants that target a fault model and for which at least one mutation operation was successfully performed.
\item{SVF}: Software Validation Facility.
\item{ADCS}: Attitude Control and Determination Software.
\item{GPS} Global Positioning System.
\item{PDHU}: Payload Data Handling Unit.

\end{itemize}

\clearpage
