% !TEX root = MAIN.tex

\chapter{Deliverables Summary}

\label{chap:deliverables_summary}

This chapter presents a summary of the deliverables of the FAQAS project; they are listed below alongside a brief summary of their content.

\begin{itemize}
	\item \emph{ITT-1-9873-ESA-FAQAS-D1}: The deliverable D1 is called ``Fault-based Automated Quality assurance of Test Suites: A Survey of Mutation Testing and Test Suite Augmentation Approaches for Satellite and Embedded Systems''. This document presents a comprehensive review of the mutation testing litrature. It also includes a list of mutation testing benchmarks and comments about the latest mutation testing trends.

	\item \emph{ITT-1-9873-ESA-FAQAS-D2}: The deliverable D2 is called ``Study of mutation testing applicability''. The document presents for each approach proposed in FAQAS (i.e., code-driven mutation analysis, code-driven mutation testing, data-driven mutation analysis, and data-driven mutation testing) a feasibility study, an assessment of the state-of-the-art, and, finally, the algorithms adopted to implement each approach in a dedicated software tool (i.e., MASS, SEMuS, DAMAt, and DAMTe).

	\item \emph{ITT-1-9873-ESA-FAQAS-D4}: The deliverable D4 is called ``Validation of the toolset''. The document presents the case study subjects considered to validate the FAQAS toolset. Moreover, the document present the setup and results of the empirical evaluation conducted to systematically evaluate each tool provided by FAQAS.

	\item \emph{ITT-1-9873-ESA-FAQAS-D5}: The deliverable D5 is called ``Evaluation of mutation testing process and methodology definition''. The document presents the methodology to assess and improve a test suite by relying on the FAQAS toolset.

	\item \emph{ITT-1-9873-ESA-FAQAS-D5-GomSpace\ Evaluation\ of\ DAMAt\ Signed}: The deliverable called ``GomSpace Evaluation of DAMAt'' reports the results of the evaluation performed by GomSpace on the FAQAS toolset DAMAt.

	\item \emph{ITT-1-9873-ESA-FAQAS-D5-GomSpace\ Evaluation\ of\ MASS\ toolset\ Signed}: The deliverable called ``GomSpace Evaluation of MASS toolset'' reports the results of the evaluation performed by GomSpace on the FAQAS toolset MASS.

	\item \emph{ITT-1-9873-ESA-FAQAS-D5-FAQ-LXS-TN-0001\_1A\ MASS\_DAMAt\_SEMuS\_Toolsets\_LXS\_Assessment}: The deliverable called ``MASS DAMAt SEMuS Toolsets LXS Assessment'' reports the results of the evaluation performed by LuxSpace on the FAQAS toolsets MASS, DAMAt, and SEMuS.

	\item \emph{ITT-1-9873-ESA-FAQAS-IRD}: The deliverable IRD is called ``Software Interface Requirements Document''. The document defines for each toolset, the external interfaces and the operational environment. The document also delivers information about the system interface requirements.

	\item \emph{ITT-1-9873-ESA-FAQAS-SCF}: The deliverable SCF is called ``Software Configuration File''. The document fully describes the software deliverables of the FAQAS project (i.e., MASS, SEMuS, DAMAt, and DAMTe), it also describes the development track platform, and lists the baseline documents of the project.

	\item \emph{ITT-1-9873-ESA-FAQAS-SDD}: The deliverable SDD is called ``Software Design Document''. The document describes for each FAQAS toolset, the software architecture, the software components design, the software behavior, the internal interface design, the external interface design, and test harness.

	\item \emph{ITT-1-9873-ESA-FAQAS-SPAP}: The deliverable SPAP is called ``Software Product Assurance and Planning''. The document fully describes the ECSS tailoring, the software development plan, the software validation plan, the software verification plan, the software maintenance plan, and the software product assurance plan.

	\item \emph{ITT-1-9873-ESA-FAQAS-SRelD}: The deliverable SRelD is called ``Software Release Document''. The document provides a status of the delivered software and lists its potential problems.

	\item \emph{ITT-1-9873-ESA-FAQAS-SRF}: The deliverable SRF is called ``Software Reuse File''. The document provides a description of the reused software in the FAQAS framework. It also includes information about the licensing of the reused components.

	\item \emph{ITT-1-9873-ESA-FAQAS-SSS}: The deliverable SSS is called ``Software System Specification''; it provides a complete list of requirements of the FAQAS toolset.

	\item \emph{ITT-1-9873-ESA-FAQAS-SUM}: The deliverable SUM is called ``Software User Manual''. The document fully describes the requirements and procedures for running the FAQAS toolset (i.e., MASS, SEMuS, DAMAt, and DAMTe). It also includes a tutorial for each of the toolset.

	\item \emph{ITT-1-9873-ESA-FAQAS-SUTP}: The deliverable SUTP is called ``Software Unit Test Plan''. The document describes the unit testing approach, the unit testing design, the unit testing specifications, and the unit testing procedures of every FAQAS tool.

	\item \emph{ITT-1-9873-ESA-FAQAS-SUTR}: The deliverable SUTR is called ``Software Unit Test Report''. The document reports the outcome of the unit testing procedures described in the SUTP document, there is a dedicated chapter for each FAQAS toolset.

	\item \emph{ITT-1-9873-ESA-FAQAS-SValR}: The deliverable SValR is called ``Software Validation Report''; it specifies, for each tool, the outcome of the validation procedures defined in the SPAP document.

	\item \emph{ITT-1-9873-ESA-FAQAS-SVS}: The deliverable SVS is called ``Software Validation Specification''. The document provides a mapping between requirements and testing procedures.
\end{itemize}
