{
\scriptsize
% Please add the following required packages to your document preamble:
% \usepackage{longtable}
% Note: It may be necessary to compile the document several times to get a multi-page table to line up properly
\begin{longtable}{|l|l|l|l|l|l|l|l|l|l|l|l|p{0.1 \textwidth}|}
\caption{Mutants that applied the mutation and were not killed by the test suite of the \case }
\label{tab:live_mutants}\\
\hline
\textbf{\#} &
\textbf{FaultModel} &
 \textbf{D.Item} &
 \textbf{Span} &
 \textbf{Type} &
 \textbf{F.Class} &
 \textbf{Min} &
 \textbf{Max} &
 \textbf{Thresh.} &
 \textbf{Delta} &
 \textbf{State} &
 \textbf{Value} &
 \textbf{Action Item}
 \\ \hline
\endfirsthead
%
\endhead
1 & IfStatus & 0 & 1 & BIN & BF & 4 & 4 & NA & NA & -1 & 1 & Check oracle for data item containing OBC communication error\\ \hline
2 & IfStatus & 0 & 1 & BIN & BF & 5 & 7 & NA & NA & -1 & 1 & Check oracle for data itemcontaining  Unit communication error\\ \hline
3 & IfStatus & 1 & 1 & BIN & BF & 0 & 4 & NA & NA & -1 & 1 & Check oracle for data item containing Unit in error\\ \hline
4 & IfStatus & 4 & 1 & BIN & BF & 0 & 2 & NA & NA & -1 & 1 & Check oracle for data item containing Gyroscope enable\\ \hline
5 & IfStatus & 4 & 1 & BIN & BF & 2 & 4 & NA & NA & -1 & 1 & Check oracle for data item containing Reaction Wheel enable\\ \hline
6 & IfStatus & 4 & 1 & BIN & BF & 5 & 7 & NA & NA & -1 & 1 & 3 Check oracle for data item containing axis Magnetorquer enable\\ \hline
8 & IfStatus & 5 & 1 & BIN & BF & 2 & 7 & NA & NA & -1 & 1 & S. Check oracle for data item containing Sensor board ADC enable\\ \hline
9 & IfHK & 12 & 2 & DOUBLE & VAT & NA & NA & 3.6 & 0.1 & NA & NA & Check oracle for data item containing VCCb\\ \hline
11 & IfHK & 14 & 2 & DOUBLE & VAT & NA & NA & 33.53 & 0.01 & NA & NA & Check oracle for data item containing VBUS\\ \hline
14 & IfHK & 14 & 2 & DOUBLE & FVBT & NA & NA & 24 & 1 & NA & NA & Check oracle for data item containing VBUS\\ \hline
15 & IfHK & 24 & 2 & DOUBLE & VAT & NA & NA & 6 & 1 & NA & NA & Check oracle for data item containing VCC Software 1\\ \hline
20 & IfHK & 30 & 2 & DOUBLE & VOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 2\\ \hline
21 & IfHK & 30 & 2 & DOUBLE & VOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 2\\ \hline
22 & IfHK & 30 & 2 & DOUBLE & FVOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 2\\ \hline
23 & IfHK & 32 & 2 & DOUBLE & VOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 3a\\ \hline
24 & IfHK & 32 & 2 & DOUBLE & VOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 3a\\ \hline
25 & IfHK & 32 & 2 & DOUBLE & FVOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 3a\\ \hline
26 & IfHK & 34 & 2 & DOUBLE & VOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 3b\\ \hline
27 & IfHK & 34 & 2 & DOUBLE & VOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 3b\\ \hline
28 & IfHK & 34 & 2 & DOUBLE & FVOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 3b\\ \hline
29 & IfHK & 36 & 2 & DOUBLE & VOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 4\\ \hline
30 & IfHK & 36 & 2 & DOUBLE & VOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 4\\ \hline
31 & IfHK & 36 & 2 & DOUBLE & FVOR & -20 & 50 & NA & 1 & NA & NA & Check oracle for data item containing PCB Temperature 4\\ \hline
32 & GYTM & 0 & 1 & BIN & BF & 0 & 0 & NA & NA & -1 & 1 & Check oracle for data item containing Unit identifier\\ \hline
33 & GYTMF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x51 & Check oracle for data item containing Error type\\ \hline
34 & GYTMF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x52 & Check oracle for data item containing Error type\\ \hline
35 & GYTMF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x53 & Check oracle for data item containing Error type\\ \hline
36 & GYTMF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x54 & Check oracle for data item containing Error type\\ \hline
37 & GYTMF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x56 & Check oracle for data item containing Error type\\ \hline
84 & S.SensorTMF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x51 & Check oracle for data item containing Error type\\ \hline
85 & S.SensorTMF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x54 & Check oracle for data item containing Error type\\ \hline
86 & S.SensorTMF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x56 & Check oracle for data item containing Error type\\ \hline
87 & SSTP & 0 & 2 & DOUBLE & VOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 3\\ \hline
88 & SSTP & 0 & 2 & DOUBLE & VOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 3\\ \hline
89 & SSTP & 0 & 2 & DOUBLE & FVOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 3\\ \hline
93 & SSTP & 4 & 2 & DOUBLE & VOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 6\\ \hline
94 & SSTP & 4 & 2 & DOUBLE & VOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 6\\ \hline
95 & SSTP & 4 & 2 & DOUBLE & FVOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 6\\ \hline
96 & SSTP & 6 & 2 & DOUBLE & VOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 5\\ \hline
97 & SSTP & 6 & 2 & DOUBLE & VOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 5\\ \hline
98 & SSTP & 6 & 2 & DOUBLE & FVOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 5\\ \hline
99 & SSTP & 8 & 2 & DOUBLE & VOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 4\\ \hline
100 & SSTP & 8 & 2 & DOUBLE & VOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 4\\ \hline
101 & SSTP & 8 & 2 & DOUBLE & FVOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 4\\ \hline
102 & SSTP & 10 & 2 & DOUBLE & VOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 7\\ \hline
103 & SSTP & 10 & 2 & DOUBLE & VOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 7\\ \hline
104 & SSTP & 10 & 2 & DOUBLE & FVOR & -70 & 100 & NA & 1 & NA & NA & Check oracle for data item containing Temperature reading from ADC 7\\ \hline
105 & SSTPF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x51 & Check oracle for data item containing Error type\\ \hline
106 & SSTPF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x54 & Check oracle for data item containing Error type\\ \hline
107 & SSTPF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x56 & Check oracle for data item containing  type\\ \hline
108 & SpaceCraftHK & 0 & 2 & DOUBLE & VAT & NA & NA & 3.3 & 0.1 & NA & NA & Check oracle for data item containing TMTC Software 1\\ \hline
110 & SpaceCraftHK & 0 & 2 & DOUBLE & VBT & NA & NA & 0 & 0.1 & NA & NA & Check oracle for data item containing TMTC Software 1\\ \hline
114 & SpaceCraftHK & 2 & 2 & DOUBLE & FVOR & 0.5 & 2.75 & NA & 0.01 & NA & NA & Check oracle for data item containing TMTC Software 2\\ \hline
170 & M.SetPWMRSPF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x51 & Check oracle for data item containing Error type\\ \hline
171 & M.SetPWMRSPF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x52 & Check oracle for data item containing Error type\\ \hline
172 & M.SetPWMRSPF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x53 & Check oracle for data item containing Error type\\ \hline
173 & M.SetPWMRSPF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x54 & Check oracle for data item containing Error type\\ \hline
174 & M.SetPWMRSPF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x56 & Check oracle for data item containing Error type\\ \hline
175 & M.SetPWMRSPF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x5d & Check oracle for data item containing Error type\\ \hline
176 & M.SetPWMRSPF. & 0 & 1 & HEX & IV & NA & NA & NA & NA & NA & 0x5e & Check oracle for data item containing Error type \\ \hline
\end{longtable}}
