% !TEX root = MAIN.tex

\chapter{Reference Manual}
\label{chapter:reference}

\REVISION{P-2}{

\section{Code-driven mutation analysis toolset (MASS)}

\MASS supports the following commands:
	\begin{itemize}
	\item \texttt{PrepareSUT}: command to prepare the SUT and collect information about the SUT test suite.
	\item \texttt{GenerateMutants}: command to generate mutants from the SUT source code.
	\item \texttt{CompileOptimizedMutants}: command to compile the mutants with the multiple optimisation levels.
	\item \texttt{OptimizedPostProcessing}: command to disregard equivalent and redundant mutants based on compiler optimisations.
	\item \texttt{GeneratePTS}: command to generate the prioritized and reduced test suites.
	\item \texttt{ExecuteMutants}: command to execute mutants against the SUT test suite.
	\item \texttt{IdentifyEquivalents}: command to identify equivalent mutants based on code coverage.
	\item \texttt{MutationScore}: command to compute the mutation score and final reporting.
	\item \texttt{PrepareMutants\_HPC}: command to prepare the mutants workspace for the execution on HPCs.
	\item \texttt{ExecuteMutants\_HPC}: command to execute mutants on HPCs.
	\item \texttt{PostMutation\_HPC}: command to assess past mutant executions, and to decide whether more mutant executions are needed.
\end{itemize}

For more information about how to operate each command, please refer to Section~\ref{sec:launchers}.

\section{Code-driven test generation toolset (\SEMUS)}

\SEMUS supports the following commands:
	\begin{itemize}
	\item \texttt{call\_generate\_direct.sh}: command to generate the test templates for guiding the test generation process.
	\item \texttt{docker\_run.sh}: command to launch the test generation process.
\end{itemize}

For more information about how to operate each command, please refer to Section~\ref{sec:semuslaunch}.

\section{Data-driven mutation analysis toolset (\DAMA)}
\begin{itemize}
\item \texttt{DAMAt\_probe\_generation.sh}: command to generate the data mutation probes.
\item \texttt{DAMAt\_mutants\_launcher.sh}: command to execute the mutants against the SUT test suite.
\end{itemize}

For more information about how to operate each command, please refer to Section~\ref{sec:dama_singlelaunch}.

\section{Data-driven test generation toolset (DAMTE)}
}
